---
title: "DKAS, multilevel logistic regression - 2016 & 2017 UD MOOCs"
author: "Bindoff, A., Eccleston, C."
output:
  github_document: default
---

`r Sys.Date()`


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = F, message = F)
options(width = 100)
```

```{r, warning = F, message = F}
# libraries can be installed by running the command install.packages(c("dplyr", "lme4", "lsmeans", "lmerTest", "foreign", "ggplot2", "reshape2"))

library(lme4)
library(lsmeans)
library(ggplot2)
library(foreign)
library(reshape2)
library(dplyr)
library(knitr)
library(xtable)
library(latticeExtra)
library(scico)
library(viridis)
```

### Logistic regression

A dummy variable was code denoting scores >=45, being the 90th percentile score at pre-test.  


```{r}
load("dkas_2016_2017")
```
  
  
  
Inter-quartile range of scores at **pre-test**   


```{r, eval = T, echo = TRUE}
quantile(filter(df0, time == "pre")$raw_score, c(0.25, 0.5, 0.75, 0.90))
```
  
Fit the logistic regression model, obtain p-values using a likelihood-ratio test.  

```{r, eval = T, echo = T}
library(optimx)
df0$score <- df0$raw_score >= 45 
m2 <- glmer(score ~ time + education + exposure + exposure:time +
              (1|subjectid) + (1|year), data = df0,
             family = binomial(link = logit), 
          control = glmerControl(optimizer ='optimx', optCtrl=list(method='nlminb')))

drop1(m2, test = "Chisq")
```


Pairwise differences estimated using Tukey contrasts to find the minimum set of pairwise differences, p-values adjusted using Tukey method to correct for multiple comparisons. 

```{r, echo = TRUE}

summary(lsmeans(m2, list(revpairwise ~ education|time)), type = "response")

summary(lsmeans(m2, list(revpairwise ~ time|exposure)), type = "response")

summary(lsmeans(m2, list(revpairwise ~ exposure|time)), type = "response")
```
